Comparison of Analytical and Artificial Neural Network models in predicting hot deformation behavior of AISI P20

### 2022-11-24 Article.tex
Add two lines in final tables

Figure \ref{fig:CompInt} shows a comparison, for strain rate $\mdot\varepsilon=1~\ps$, of the flow stresses $\sigma^y$ calculated by the models (as a line) and the experimental results (as points) for the 5 analytical models and the neural network.
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]
{Figures/CompInt}
\caption{Comparison between the experimental (dot) and predicted flow stresses $\sigma^y$ (lines) for $\mdot\varepsilon=1~\ps$}
\label{fig:CompInt}
\end{figure}
Table \ref{tab:IntVal} shows the $\AARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the 6 strain rates (lines referred as: all) or only on the strain rate $\mdot\varepsilon=1~\ps$.
\begin{table}[h!]
\centering{}
\caption{Accuracy coefficients of interpolation for all models $\mdot\varepsilon=1~\ps$}
\begin{tabular}{llcccccc}
\hline
$\mdot\varepsilon$               & Coefficients        & JC      & MZA     & HS     & AR     & PTM    & ANN\\
\hline
\mr{2}{all}                      & $\AARE(\%)$         & $13.97$ & $21.49$ & $7.76$ & $3.54$ & $4.78$ & $0.78$\\
                                 & $\RMSE(\text{MPa})$ & $11.86$ & $19.86$ & $3.84$ & $2.17$ & $4.45$ & $0.71$\\\hline
\mr{2}{$\mdot\varepsilon=1~\ps$} & $\AARE(\%)$         & $14.87$ & $27.79$ & $3.74$ & $1.46$ & $3.16$ & $1.40$\\
                                 & $\RMSE(\text{MPa})$ & $12.02$ & $23.67$ & $3.10$ & $1.46$ & $2.65$ & $1.52$\\
\hline
\label{tab:IntVal}
\end{tabular}
\end{table}

@@

From a general appearance point of view, the other 4 models, HS, AR, PTM and ANN, give globally similar results with a higher fidelity for the AR and ANN models compared to the other two models.
Table \ref{tab:IntVal} shows the quantitative comparison on all the deformation speeds and on $\mdot\varepsilon=1~\ps$ for these 4 models.
It appears from this Table that if the two models AR and ANN give equivalent (and excellent) results concerning the values of $\AARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=1~\ps$, the ANN model gives globally a better result on the whole of the strain rates with values of $\AARE=0.78\%$ and $\RMSE=0.71~\text{MPa}$ respectively, that is to say values approximately 3 times lower for the ANN model compared to the AR model.

@@

In this new identification configuration, Figure \ref{fig:CompExt} shows a comparison, for strain rate $\mdot\varepsilon=5~\ps$, of the flow stresses $\sigma^y$ computed by the models (as a line) and the experimental results (as points) for the 5 analytical models and the neural network.
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]
{Figures/CompExt}
\caption{Comparison between the experimental (dot) and predicted flow stresses $\sigma^y$ (lines) for $\mdot\varepsilon=5~\ps$}
\label{fig:CompExt}
\end{figure}
Table \ref{tab:ExtVal} shows the $\AARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the 6 strain rates (lines referred as: all) or only on the strain rate $\mdot\varepsilon=5~\ps$.
%For the validation of the extrapolation, the chosen strain rate is $\mdot\varepsilon = 5.0~\ps$ and those used for identification (training for ANN) are $\mdot\varepsilon = 0.001~\ps$ , $\mdot\varepsilon = 0.01~\ps$ , $\mdot\varepsilon = 0.1~\ps$, $\mdot\varepsilon = 1.0~\ps$  and $\mdot\varepsilon = 2.0~\ps$.
%Figure \ref{fig:CompExt} shows the comparison between the predictions  and the experimental.
%Unlike interpolation, the predictions of the analytical models are not very good because the errors are between $3.2\%$ and $12.99\%$ while that of the ANN model is $1.74\%$.
%Again, the ANN model shows its ability to extrapolate data.
%This makes it possible to say that the ANN model remains the best tool to characterize the behavior of a material subjected to certain deformation conditions.
%It can also be noted that the Arrhenius and the PTM models still have some ability to extrapolate because their $\AARE$ are respectively $ 3.2 \% $ and $ 3.8 \%$; which are acceptable.
\begin{table}[h!]
\centering{}
\caption{Accuracy coefficients of extrapolation for all models $\mdot\varepsilon=5~\ps$}
\begin{tabular}{llcccccc}
\hline
$\mdot\varepsilon$               & Coefficients        & JC      & MZA     & HS     & AR     & PTM     & ANN\\
\hline
\mr{2}{all}                      & $\AARE(\%)$         & $15.12$ & $25.87$ & $7.37$ & $3.95$ & $5.53$  & $1.15$\\
                                 & $\RMSE(\text{MPa})$ & $12.36$ & $18.24$ & $4.43$ & $2.68$ & $6.23$  & $2.40$\\\hline
\mr{2}{$\mdot\varepsilon=5~\ps$} & $\AARE(\%)$         & $20.16$ & $24.27$ & $7.37$ & $3.53$ & $11.46$ & $3.87$\\
                                 & $\RMSE(\text{MPa})$ & $20.73$ & $25.95$ & $7.83$ & $4.02$ & $12.91$ & $5.84$\\
\hline
\label{tab:ExtVal}
\end{tabular}
\end{table}

@@

The other 4 models, HS, AR, PTM and ANN, give better results with higher fidelity for the AR and ANN models compared to the other two models.
Table \ref{tab:ExtVal} shows the comparison over all strain rates and over $\mdot\varepsilon=5~\ps$ for these 4 models.
The HS model performs worse on extrapolation than the AR and ANN models, while the PTM model is relegated to the last position in this ranking with values of $\AARE$ and $\RMSE$ superior to $10\%$ for the strain rate $\mdot\varepsilon=5~\ps$.
The two models AR and ANN give the best results concerning the values of $\AARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=5~\ps$.
The AR model is this time a little bit better on the $\mdot\varepsilon=5~\ps$ strain rate compared to the ANN model, but the latter gives globally a better result on the whole strain rates with values of  $\AARE=1.15\%$ and $\RMSE=2.40~\text{MPa}$ respectively.

>>>>

Figure \ref{fig:CompInt} shows a comparison, for strain rate $\mdot\varepsilon=1~\ps$, of the flow stresses $\sigma^y$ calculated by the models (as a line) and the experimental results (as points) for the 5 analytical models and the neural network.
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]
{Figures/CompInt}
\caption{Comparison between the experimental (dot) and predicted flow stresses $\sigma^y$ (lines) for $\mdot\varepsilon=1~\ps$}
\label{fig:CompInt}
\end{figure}
Table \ref{tab:IntVal} shows the $\AARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the 6 strain rates (lines referred as: all) or only on the strain rate $\mdot\varepsilon=1~\ps$.
\begin{table}[h!]
\centering{}
\caption{Accuracy coefficients of interpolation for all models with  $\mdot\varepsilon=1~\ps$}
\begin{tabular}{llcccccc}
	\hline
	$\mdot\varepsilon$               & Coefficients        &   JC    &   MZA   &   HS   &   AR   &  PTM   &  ANN   \\ \hline
	\mr{2}{id. $\mdot\varepsilon$}   & $\AARE(\%)$         & $13.79$ & $20.22$ & $8.57$ & $3.96$ & $5.10$ & $0.70$ \\
	                                 & $\RMSE(\text{MPa})$ & $11.83$ & $19.00$ & $3.97$ & $2.29$ & $4.73$ & $0.38$ \\ \hline
	\mr{2}{$\mdot\varepsilon=1~\ps$} & $\AARE(\%)$         & $14.87$ & $27.79$ & $3.74$ & $1.46$ & $3.16$ & $2.47$ \\
	                                 & $\RMSE(\text{MPa})$ & $12.02$ & $23.67$ & $3.10$ & $1.46$ & $2.65$ & $2.77$ \\ \hline
	\mr{2}{all $\mdot\varepsilon$}   & $\AARE(\%)$         & $14.42$ & $28.90$ & $7.55$ & $3.45$ & $4.90$ & $0.96$ \\
	                                 & $\RMSE(\text{MPa})$ & $11.86$ & $19.86$ & $3.84$ & $2.17$ & $4.45$ & $1.18$ \\ \hline
	\label{tab:IntVal}               &
\end{tabular}
\end{table}

@@

From a general appearance point of view, the other 4 models, HS, AR, PTM and ANN, give globally similar results with a higher fidelity for the AR and ANN models compared to the other two models.
Table \ref{tab:IntVal} shows the quantitative comparison on $\AARE$ and $\RMSE$ for three different cases: on the 5 identified strain rates, on only the strain rate $\mdot\varepsilon=1~\ps$ and on all 6 strain rates for these 6 models.
It appears from this Table that if the two models AR and ANN give equivalent (and excellent) results concerning the values of $\AARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=1~\ps$, the ANN model gives globally a better result on the whole of the strain rates with values of $\AARE=0.96\%$ and $\RMSE=1.18~\text{MPa}$ respectively, that is to say values approximately 2 to 3 times lower for the ANN model compared to the AR model.

@@

In this new identification configuration, Figure \ref{fig:CompExt} shows a comparison, for strain rate $\mdot\varepsilon=5~\ps$, of the flow stresses $\sigma^y$ computed by the models (as a line) and the experimental results (as points) for the 5 analytical models and the neural network.
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]
{Figures/CompExt}
\caption{Comparison between the experimental (dot) and predicted flow stresses $\sigma^y$ (lines) for $\mdot\varepsilon=5~\ps$}
\label{fig:CompExt}
\end{figure}
Table \ref{tab:ExtVal} shows the $\AARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the 6 strain rates (lines referred as: all) or only on the strain rate $\mdot\varepsilon=5~\ps$.
\begin{table}[h!]
\centering{}
\caption{Accuracy coefficients of extrapolation for all models with  $\mdot\varepsilon=5~\ps$}
\begin{tabular}{llcccccc}
\hline
$\mdot\varepsilon$               & Coefficients        & JC      & MZA     & HS     & AR     & PTM     & ANN\\
\hline
\mr{2}{id. $\mdot\varepsilon$}   & $\AARE(\%)$         & $13.09$ & $19.09$ & $7.30$ & $4.03$ & $4.34$  & $0.61$\\
                                 & $\RMSE(\text{MPa})$ & $9.86$  & $16.26$ & $3.36$ & $2.32$ & $3.63$  & $0.32$\\\hline
\mr{2}{$\mdot\varepsilon=5~\ps$} & $\AARE(\%)$         & $20.16$ & $24.27$ & $7.73$ & $3.53$ & $11.46$ & $3.87$\\
                                 & $\RMSE(\text{MPa})$ & $20.73$ & $25.95$ & $7.83$ & $4.02$ & $12.91$ & $5.84$\\\hline
\mr{2}{all $\mdot\varepsilon$}   & $\AARE(\%)$         & $15.12$ & $25.87$ & $7.12$ & $3.86$ & $5.34$  & $1.09$\\
                                 & $\RMSE(\text{MPa})$ & $12.36$ & $18.24$ & $4.43$ & $2.68$ & $6.23$  & $2.40$\\\hline
\label{tab:ExtVal}
\end{tabular}
\end{table}

@@

The other 4 models, HS, AR, PTM and ANN, give better results with higher fidelity for the AR and ANN models compared to the other two models.
Table \ref{tab:ExtVal} shows the comparison over all strain rates and over $\mdot\varepsilon=5~\ps$ for these 6 models.
The HS model performs worse on extrapolation than the AR and ANN models, while the PTM model is relegated to the last position in this ranking with values of $\AARE$ and $\RMSE$ superior to $10\%$ for the strain rate $\mdot\varepsilon=5~\ps$.
The two models AR and ANN give the best results concerning the values of $\AARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=5~\ps$.
The AR model is this time a little bit better on the $\mdot\varepsilon=5~\ps$ strain rate compared to the ANN model, but the latter gives globally a better result on the whole strain rates with values of  $\AARE=1.09\%$ and $\RMSE=2.40~\text{MPa}$ respectively.
